Ao's Notes on Medical Imaging Software

### 2020-03-01 StateOfPractice/Ao-Notes/Ao-Notes.tex
Relocate to a new folder

Link to the software list (Google Sheet): \href{https://docs.google.com/spreadsheets/d/122wU0v3ZtvDcqy8C4zKJ89kU-8fXAbo3Mzn6vcVXOi0/edit?usp=sharing}{LINK}

>>>>

The link to the software list (Google Sheet): \href{https://docs.google.com/spreadsheets/d/122wU0v3ZtvDcqy8C4zKJ89kU-8fXAbo3Mzn6vcVXOi0/edit?usp=sharing}{LINK}

\noindent There are 50 packages in the list.

\subsection{Sources}

The above list is built based on 7 sources - 3 academical papers, 3 blog articles, and 1 online forum discussion. All of the sources are recorded on the second sheet in the list.

\subsection{Orders}

The software packages are put in the list roughly by the order of how many times they are mentioned in the above sources.

\subsection{Selection}

A few software packages mentioned in the sources are excluded, since they are in the following cases:
\begin{itemize}
    \item Commercialized. Some software are not free any more. For example, PacsOne Premium, JVS-DiComPlus, RadiAnt, Synedra, TurtleSeg, AlgoM, Athena.
    \item No recent updates. A few software without recent release are excluded, such as PacsOne Basic (2005), K-PACS (developed for Windows XP or Windows VISTA), JVS-DiCom (2012), MITO-DICOM Viewer (2015), Aeskulap (2007), Fusionviewer (2008), Kradview (2013), Mayam (2013), Eviewbox (2015), EzDICOM (2013), Agnosco (2011), ONIS Free Version (2016 and not open-source), DICOMscope (2001).
\end{itemize}

\subsection{Categories}

The software packages are roughly divided into 3 major categories - Tool Kit, PACS, and Viewer.
\begin{itemize}
    \item Tool Kits are usually used by developers to create new software, and there are only a few of them in the list. 
    \item PACS stands for Picture Archiving and Communications System, which can be regarded as a type of server. There are also only several of them in the list, since most PACS solutions are commercial nowadays.
    \item  Most software in the list are in the Viewer category, and many of these ones also provide other functions such as analysis, conversion, segmentation, etc.
\end{itemize}
